Stat 400 Project

### 2021-12-04 Stat 400 proj.Rmd
added more of nates code that didn't pull
it says i need to commit
basic recovery time update

  #pregenerated days of recovery times for each person
  recovery_days <- rpois(num_subjects,14)
  inc_time <- rpois(num_subjects,5)

  #Put into a data frame
  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects,recovery_days,inc_time))
  colnames(df)[1] <- 'x'
  colnames(df)[2] <- 'y'
  colnames(df)[3] <- 'subjects'
  colnames(df)[4] <- 'recovery'
  colnames(df)[5] <- 'incubation'
  return(df)
}

@@

#Function for deciding if infections occurred
#BUG -- If the mean_crit_dist is small, all infections go away!!
infection_status <- function(state, mean_crit_dist,t){

@@

      z_s <- as.numeric(current_rec_time[i])

@@

      if(d <= crucial_distance){
        new_status[j] <- 'I'
        newly_infected <- c(newly_infected, j)
      }

      #check recovery time for person at z_s. If their recovery day time is past the current day, they recovered. 
      if(z_s>=t){
        new_status[j] <- 'Rec'
      }

      else{
        new_status[j] <- 'S'
      }
    }
  }

  current_non_infected[newly_infected, 3] <- 'I'
  new_state <- rbind(current_infected, current_non_infected)

  # new_state <- c(new_status, current_infected[,3])
  return(new_state)
}

@@

      updated_positions <- update_coords(initial_data, change)
      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      new_status <- infection_status(checked_positions, 2,i)
      checked_positions[,3] <- new_status
      end_day[[i]] <- checked_positions

      updated_positions <- update_coords(initial_data, change)#, x_dim, y_dim)x_dim,y_dim not parameters
      # checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      updated_state <- cbind(updated_positions, initial_data[,3])

      new_status <- infection_status(updated_state, 2)

      end_day[[i]] <- cbind(updated_positions, new_status)
    }
    else{
      step_size <- get_step_length(initial_data, x_dim, y_dim)
      direction <- get_step_direction(step_size)
      change <- get_delts(step_size, direction)

      updated_positions <- update_coords(end_day[[i-1]], change)
      checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      new_status <- infection_status(checked_positions, 1/5,i)
      checked_positions[,3] <- new_status
      end_day[[i]] <- checked_positions

      updated_positions <- update_coords(end_day[[i-1]], change)#, x_dim, y_dim) #x_dim,y_dim not parameters in update_coords
      updated_state <- cbind(updated_positions, end_day[[i-1]]$new_status)

      rand_recovery_time <- rpois(1,14)
      new_status <- infection_status(updated_state, 1/5,i,rand_recovery_time)

      end_day[[i]] <- cbind(updated_positions, new_status)
    }
  }
  return(end_day[[3]])
}

>>>>

  #Create null incubation and recovery time columns
  #inc_time <- rep(NA, num_subjects)
  #rec_time <- rep(NA, num_subjects)

  inc_time <- rep(-1,num_subjects)
  rec_days <- rep(-1,num_subjects)

  #Put into a data frame
  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects,recovery_days,inc_time))
  colnames(df)[1] <- 'x'
  colnames(df)[2] <- 'y'
  colnames(df)[3] <- 'subjects'
  colnames(df)[4] <- 'incubation'
  colnames(df)[5] <- 'recovery'
  return(df)
}

@@

#Function for deciding if infections occurred
#BUG -- If the mean_crit_dist is small, all infections go away!!

#t = the current day, rt is df of recovery times. 
infection_status <- function(state, mean_crit_dist){

@@

@@

      if(d <= crucial_distance){
        newly_infected <- c(newly_infected, j)
      }
    }
  }
  current_non_infected[newly_infected, 3] <- 'I'
  current_non_infected[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 5)
  current_non_infected[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)
  new_state <- rbind(current_infected, current_non_infected)
  return(new_state)
}

@@

      updated_positions <- update_coords(initial_data, change)
      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      new_status <- infection_status(checked_positions, 2)

      not_recovered = new_status[new_status[,5]>=0]
      other = new_status[new_status[,5]<0]

      new_status = rbind(non_recovered[,5]-1,other)

      end_day[[i]] <- new_status

    }

    else{
      step_size <- get_step_length(initial_data, x_dim, y_dim)
      direction <- get_step_direction(step_size)
      change <- get_delts(step_size, direction)

      updated_positions <- update_coords(end_day[[i-1]], change)
      checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      new_status <- infection_status(checked_positions, 1/5)

      not_recovered = new_status[new_status[,5]>=0]
      other = new_status[new_status[,5]<0]

      new_status = rbind(non_recovered[,5]-1,other)

      end_day[[i]] <- new_status

    }
  }
  return(end_day[[3]])
}
